Modelling the Lymphatic Metastatic Progression Pathways of OPSCC from Multi-Institutional Datasets

### 2023-11-30 src/tex/ms.tex
[showyourwork] overleaf sync

\begin{figure}
    \script{thermo_int.py}
    \centering
    \includegraphics[width=\linewidth]{figures/thermo_int.png}
    \caption{The expected log-accuracy under the power posterior plotted against the value of the inverse temperature $\beta$. These values were computed during a \gls{ti} run for the base graph model (red line), as well as the winning graph model (green line). Note that the scaling of the x-axis is chosen such that the 64 points on the temperature ladder appear evenly spaced. This is to stress how the log-accuracy develops in the range from $\beta=0$ to around $\beta=0.1$. The area under these two curves yields an approximation of the log-evidence of the respective model. In this plot one can see that due to the simplicity of the base graph model its accuracy increases earlier and faster that the winning graph model's. However, already around $\beta=0.1$ the model based on the winning graph outperforms the base graph model. Ultimately, the winning graph's log-evidence is better than the base graph model's by a value of around \variable{output/evidence_diff.txt} (see \cref{table:evidence}).}
    \label{fig:thermo_int}
\end{figure}

>>>>

\begin{figure}
    \script{thermo_int.py}
    \centering
    \includegraphics[width=\linewidth]{figures/thermo_int.png}
    \caption{The expected log-accuracy under the power posterior plotted against the value of the inverse temperature $\beta$. These values were computed during a \gls{ti} run for the loosing graph model (red line), as well as the winning graph model (green line). Note that the scaling of the x-axis is chosen such that the 64 points on the temperature ladder appear evenly spaced. This is to stress how the log-accuracy develops in the range from $\beta=0$ to around $\beta=0.1$. The area under these two curves yields an approximation of the log-evidence of the respective model. This plot one indicates that due to the simplicity of the loosing graph model its accuracy increases earlier and faster that the winning graph model's. However, already before $\beta=0.031$ the model based on the winning graph outperforms the loosing graph model. Ultimately, the winning graph's log-evidence is better than the loosing graph model's by a value of around \variable{output/evidence_diff.txt} (see \cref{table:evidence}).}
    \label{fig:thermo_int}
\end{figure}
